Dynamics Analysis: The Sound of Teaching Music 1

### 2022-06-28 experiment-1/analysis/stats/dynamics.Rmd
update dynamics (chunk option)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### [Sequence plot](#sequence)

- [Additional analysis based on reviewers' comments](#additional)

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# statistics
if (!require("afex")) {install.packages("afex"); require("afex")}
if (!require("emmeans")) {install.packages("emmeans"); require("emmeans")}
```

>>>>

## [Sequence plot](#sequence)

## [Additional analysis](#additional)

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# statistic
if (!require("afex")) {install.packages("afex"); require("afex")}
if (!require("emmeans")) {install.packages("emmeans"); require("emmeans")}

# chunk option
knitr::opts_chunk$set(warning = FALSE)
```
